Algorithmic Approaches to Match Degraded Land Impressions

### 2017-10-06 response.Rmd

---
title: "Reviewer Response and Acknowledgment"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "October 5th, 2017"
output:
  pdf_document: default
bibliography: references.bib
---

# Acknowledgment

We wanted to begin by acknowledging the reviewers. The reviews were very thorough and immensely helpful despite being done in a very short time frame. We greatly appreciate the extra effort put forth in order to help us get this manuscript included in the special issue.

This great feedback has allowed us to effectively revise the paper. We hope that you find the revised version of the manuscript substantially improved. Below, we have addressed the individual points raised by the two reviewers.

### 2017-10-06 degraded-paper.tex
Small references change
Acknowledgment

where \(M\) is the event that two bullets match, \(NM\) is the event
that two bullets do not match, \(M1\), \(M2\), \ldots{}, \(M6\) are the
probabilities of land one, land two, \ldots{}, land six matching, and
\(NM1\), \(NM2\), \ldots{}, \(NM6\) are the probabilities that land one,
land two, \ldots{}, land six do not match. However, to compute this
probability, we need to know the alignment of the two sets of lands.
Fortunately, the consistent rotation of the bullet permits this. For
instance, if we knew that land 1 of bullet 1 matches land 4 of bullet 2,
then we immediately know that land 2 of bullet 1 matches to land 5 of
bullet 2, land 3 of bullet 1 matches to land 6 of bullet 2, etc. Hence,
we can take look across six diagonals of the \(6 \otimes 6\) matrix
containing match probabilities. Table \ref{tab:diag} gives an example of
the matrix of matching probabilities between two sets of six lands from
bullets that are known matches. The matching diagonal is clear based on
the high probabilities (cell \((1, 3)\), cell \((2, 4)\), cell
\((3, 5)\), etc.) although it can be seen that one of the six
comparisons has a relatively lower matching probability. This procedure
is based on the Sequence Average Maximum (SAM) by Sensorfar (2017) in
their bullet matching software application \texttt{SensoMatch}. A
similar approach using the cross correlation maximum was first proposed
by W. Chu et al. (2010). Compared to that approach, ours uses random
forest based probabilities compared to correlation values allowing for
elements of probability theory to help determine the resulting bullet
match probability.

@@

@@

\hypertarget{ref-sensofar}{}
Sensorfar. 2017. \emph{SensoMATCH Bullet Comparison Software}.

>>>>

where \(M\) is the event that two bullets match, \(NM\) is the event
that two bullets do not match, \(M1\), \(M2\), \ldots{}, \(M6\) are the
probabilities of land one, land two, \ldots{}, land six matching, and
\(NM1\), \(NM2\), \ldots{}, \(NM6\) are the probabilities that land one,
land two, \ldots{}, land six do not match. However, to compute this
probability, we need to know the alignment of the two sets of lands.
Fortunately, the consistent rotation of the bullet permits this. For
instance, if we knew that land 1 of bullet 1 matches land 4 of bullet 2,
then we immediately know that land 2 of bullet 1 matches to land 5 of
bullet 2, land 3 of bullet 1 matches to land 6 of bullet 2, etc. Hence,
we can take look across six diagonals of the \(6 \otimes 6\) matrix
containing match probabilities. Table \ref{tab:diag} gives an example of
the matrix of matching probabilities between two sets of six lands from
bullets that are known matches. The matching diagonal is clear based on
the high probabilities (cell \((1, 3)\), cell \((2, 4)\), cell
\((3, 5)\), etc.) although it can be seen that one of the six
comparisons has a relatively lower matching probability. This procedure
is based on the Sequence Average Maximum (SAM) by Sensofar (2017) in
their bullet matching software application \texttt{SensoMatch}. A
similar approach using the cross correlation maximum was first proposed
by W. Chu et al. (2010). Compared to that approach, ours uses random
forest based probabilities compared to correlation values allowing for
elements of probability theory to help determine the resulting bullet
match probability.

@@

\section{Acknowledgment}\label{acknowledgment}

We wish to acknowledge the anonymous reviewers, whose quick yet thorough
and immensely helpful reviews helped us improve this manuscript. We
greatly appreciate the extra effort put forth for us.

@@

\hypertarget{ref-sensofar}{}
Sensofar. 2017. \emph{SensoMATCH Bullet Comparison Software}.
